---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Time-varying correlation of SA REITs and ALSI Equities"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Andrew Hyde # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Stellenbosch University, South Africa" # First Author's Affiliation
Email1: "23365935\\@sun.ac.za" # First Author's Email address

# Author2: "John Smith"
# Ref2: "Some other Institution, Cape Town, South Africa"
# Email2: "John\\@gmail.com"
# CommonAffiliation_12: TRUE # If Author 1 and 2 have a common affiliation. Works with _13, _23, etc.
# 
# Author3: "John Doe"
# Email3: "Joe\\@gmail.com"

CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
keywords: "Multivariate GARCH \\ALSI \\REITs" # Use \\sep to separate
#JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  Abstract to be written here.
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# load pacakges to be used in the analysis
pacman::p_load("tidyverse", "devtools", "rugarch", "rmgarch", 
    "forecast", "tbl2xts", "lubridate", "PerformanceAnalytics", 
    "ggthemes", "ks", "MTS", "robustbase")

################################################################################

# read in the data
data_ALSI_returns <- read_rds("data/Alsi_Returns.rds")
# Remove the 'SJ' and 'Equity' from Tickers
data_ALSI_returns$Tickers <- gsub("SJ|Equity", "", data_ALSI_returns$Tickers)
# there are many NAs/NaNs that could pose a problem when using the mGARCH model
# therefore I log the Returns before imputing missing values i.e. NA/NaN
data_alsi <- data_ALSI_returns %>% 
    mutate(Weighted_Returns = Return * J433) %>% 
    select(date, Tickers, Weighted_Returns, Sector, J433) %>% 
    mutate(Return = log(Weighted_Returns)) %>% 
    arrange(date, Tickers) 
    #filter(date >= as.Date("2012-01-01") & date <= as.Date("2022-10-31"))

# always view the data before starting with the analysis
# replace '-Inf' with NA, so that a value is imputed when the 'impute_missig_value' fucntion is run
data_alsi[data_alsi == -Inf] <- NA

################################################################################

# source in fuctions
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))


```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}






#  Methodology \label{Meth}

## Subsection
Ideally do not overuse subsections. It equates to bad writing.^[This is an example of a footnote by the way. Something that should also not be overused.]

## Math section

Equations should be written as such:

\begin{align}
\beta = \sum_{i = 1}^{\infty}\frac{\alpha^2}{\sigma_{t-1}^2} \label{eq1} \\
\int_{x = 1}^{\infty}x_{i} = 1 \notag
\end{align}

If you would like to see the equations as you type in Rmarkdown, use $ symbols instead (see this for yourself by adjusted the equation):

$$
\beta = \sum_{i = 1}^{\infty}\frac{\alpha^2}{\sigma_{t-1}^2} \\
\int_{x = 1}^{\infty}x_{i} = 1
$$

Note again the reference to equation \ref{eq1}. Writing nice math requires practice. Note I used a forward slashes to make a space in the equations. I can also align equations using  __\&__, and set to numbering only the first line. Now I will have to type ``begin equation'' which is a native \LaTeX command. Here follows a more complicated equation:


\begin{align}
	y_t &= c + B(L) y_{t-1} + e_t   \label{eq2}    \\ \notag
	e_t &= H_t^{1/2}  z_t ; \quad z_t \sim  N(0,I_N) \quad \& \quad H_t = D_tR_tD_t \\ \notag
		D_t^2 &= {\sigma_{1,t}, \dots, \sigma_{N,t}}   \\ \notag
		\sigma_{i,t}^2 &= \gamma_i+\kappa_{i,t}  v_{i, t-1}^2 +\eta_i  \sigma_{i, t-1}^2, \quad \forall i \\ \notag
		R_{t, i, j} &= {diag(Q_{t, i, j}}^{-1}) . Q_{t, i, j} . diag(Q_{t, i, j}^{-1})  \\ \notag
		Q_{t, i, j} &= (1-\alpha-\beta)  \bar{Q} + \alpha  z_t  z_t'  + \beta  Q_{t, i, j} \notag
\end{align}

Note that in \ref{eq2} I have aligned the equations by the equal signs. I also want only one tag, and I create spaces using ``quads''.

See if you can figure out how to do complex math using the two examples provided in \ref{eq1} and \ref{eq2}.

<!-- $$ -->
<!-- This is a commented out section in the writing part. -->
<!-- Comments are created by highlighting text, amnd pressing CTL+C -->
<!-- \\begin{align} -->
<!-- \\beta = \\alpha^2 -->
<!-- \end{align} -->
<!-- $$ -->

# Results

Tables can be included as follows. Use the _xtable_ (or kable) package for tables. Table placement = H implies Latex tries to place the table Here, and not on a new page (there are, however, very many ways to skin this cat. Luckily there are many forums online!).


\hfill

<!-- hfill can be used to create a space, like here between text and table. -->


## Huxtable

Huxtable is a very nice package for making working with tables between Rmarkdown and Tex easier.

This cost some adjustment to the Tex templates to make it work, but it now works nicely.

See documentation for this package [here](https://hughjonesd.github.io/huxtable/huxtable.html). A particularly nice addition of this package is for making the printing of regression results a joy (see [here](https://hughjonesd.github.io/huxtable/huxtable.html#creating-a-regression-table)). Here follows an example:


If you are eager to use huxtable, comment out the Huxtable table in the Rmd template, and uncomment the colortbl package in your Rmd's root.

Note that I do not include this in the ordinary template, as some latex users have complained it breaks when they build their Rmds (especially those using tidytex - I don't have this problem as I have the full Miktex installed on mine). Up to you, but I strongly recommend installing the package manually and using huxtable. To make this work, uncomment the _Adding additional latex packages_ part in yaml at the top of the Rmd file. Then comment out the huxtable example in the template below this line. Reknit, and enjoy.

```{r, results = 'asis'}

if(!require(huxtable)) install.packages(huxtable)
library(huxtable)
data(diamonds, package = 'ggplot2')
Title <- "Regression Output"
Label <- "Reg01"
lm1 <- lm(price ~ carat, diamonds)
lm2 <- lm(price ~ depth, diamonds)
lm3 <- lm(price ~ carat + depth, diamonds)
htab <-
huxreg(lm1, lm2, lm3,
                statistics = c(N = "nobs", R2 = "r.squared"),
                note = "%stars%.") %>%
  set_caption(Title) %>%
  set_label(Label)
# More settings:
font_size(htab) <- 12
# Let's change regression names: this is slightly hacky, but works. Comment out this section to see what the default looks like:
  Names <- c( "Reg1", "Reg2", "Reg3")
  for(i in 1:length(Names)) {
    htab[1,][[1+i]] <- Names[i]
  }
# Now simply call the table:
htab

```

FYI - R also recently introduced the gt package, which is worthwhile exploring too.

# Lists

To add lists, simply using the following notation

* This is really simple

    + Just note the spaces here - writing in R you have to sometimes be pedantic about spaces...

* Note that Rmarkdown notation removes the pain of defining \LaTeX environments!

# Conclusion

I hope you find this template useful. Remember, stackoverflow is your friend - use it to find answers to questions. Feel free to write me a mail if you have any questions regarding the use of this package. To cite this package, simply type citation("Texevier") in Rstudio to get the citation for @Texevier (Note that uncited references in your bibtex file will not be included in References).

<!-- Make title of bibliography here: -->
<!-- \newpage -->

\newpage

# References {-}

<div id="refs"></div>


# Appendix {-}

## Appendix A {-}

Some appendix information here

## Appendix B {-}

